openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Update my affiliation

---
title: "openarchaeoCollaboration"
author:
  - name: Zack Batist
    url: https://zackbatist.github.io
    affiliation: University of Toronto
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: University of Copenhagen
date: "`r Sys.Date()`"
---

>>>>

---
title: "openarchaeoCollaboration"
author:
  - name: Zack Batist
    url: https://zackbatist.github.io
    affiliation: University of Toronto
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: University of Bern
date: "`r Sys.Date()`"
---
